### 2017-08-02 Paper01_EnthalpyAndCrystallization.tex
Results - DSC - Draft for bulk DSC done

%\documentclass[a4paper,12pt,oneside]{article}%FinalView
\documentclass[draft,a4paper,12pt,oneside]{article}%draftView

@@

@@

\subsection{\acrshort{dsc}}
\subsubsection{Isothermal \acrshort{dsc}}

>>>>

\documentclass[a4paper,12pt,oneside]{article}%FinalView
%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView

@@

Isothermal relaxation \acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.

@@

\subsection{\acrshort{dsc}}
\subsubsection{Isothermal \acrshort{dsc}}
Isothermal \acrshort{dsc} was performed on the bulk and film \MgZnCa~ to examine the thermal properties. The bulk alloy was relaxed at $120$\degree C for 10 minutes before \acrshort{dsc} measurements to ensure the \Tg~ was clearly visible. The film was not relaxed as unlike the bulk the lost in free volume from relaxation would be significant and make differences between the samples much more difficult to observe [source needed???].

The bulk \MgZnCa~ was examined at \glspl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and \Tx s with \gls{ht}. As expected greater \gls{ht} resulted in greater signal strength, exothermic peaks shifting to higher start temperatures, and an increase in thermal lag resulting in later exothermic finish temperatures and curve convolution. With this convolution the \Tg~ and \Tx $_{1}$  remained clearly visible for all \glspl{ht}, but \Tx $_{2,4,5}$ were only visible at low \glspl{ht}, and \Tx $_{3}$ was not clear at any \gls{ht}, see Figure \ref{fig:DSC_vHeatingRate_Bulk}.

START HERE. Likely talking about Films!!!
Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates (\acrshort{ht}) to observe changed in the \Tg~ and \Tx~ temperatures. As expected higher heating rates resulted in great signal strength, exothermic peaks shifting to higher temperatures, and increases in thermal lag resulting in curve convolution.
